Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-03-11 hb.tex
update syntax to v0.9.0

The first version of our hierarchy (that we name V1) features only two
structures: \coq{Monoid} and \coq{Ring}.
%\marginpar{remove hb.end for \mixins{}, use next release of coq elpi}
\begin{coqcode}
#\hbmixin{}# Record Monoid_of_Type A := {                       #\label{demo:mixin:mot}#
  zero : A;
  add : A -> A -> A;
  addrA : associative add;             (* `add` is associative.                   *)
  add0r : left_id zero add;            (* `zero` is the left and right neutral    *)
  addr0 : right_id zero add;           (*   element with respect to `add`.        *)
}.                                                             #\label{demo:mixin:mot:end}#
#\hbstructure{}# Definition Monoid := { A of Monoid_of_Type.axioms A }.        #\label{demo:structure:monoid}#

#\hbmixin{}# Record Ring_of_Monoid A of Monoid.axioms A := {       #\label{demo:mixin:rom}#
  one : A;
  opp : A -> A;
  mul : A -> A -> A;
  addNr : left_inverse zero opp add;   (* `opp x` is the left and right additive  *)
  addrN : right_inverse zero opp add;  (*   inverse of `x`.                       *)
  mulrA : associative mul;             (* `mul` is associative.                   *)
  mul1r : left_id one mul;             (* `one` is the left and right neutral     *)
  mulr1 : right_id one mul;            (*   element with respect to `mul`.        *)
  mulrDl : left_distributive mul add;  (* `mul` is left and right distributive    *)
  mulrDr : right_distributive mul add; (*   over `add`.                           *)
}.
#\hbstructure{}# Definition Ring := { A of Monoid.axioms A & Ring_of_Monoid.axioms A }. #\label{demo:structure:ring}#

@@

Line~\ref{demo:mixin:rom} declares a second \mixin{} collecting the operations
and properties that are needed in order to enrich a monoid to a ring, hence
the name \coq{Ring_of_Monoid}. Indeed this time the type variable \coq{A}
is followed by \coq{Monoid.axioms} that enriches
\coq{A} with the operations and properties of monoids. As a consequence
\coq{add} and \coq{zero} can be used to express the new properties.

@@

Definition Z_Monoid_axioms : Monoid_of_Type.axioms Z :=                         #\label{demo:theory:z:monoid:axioms}#
  Monoid_of_Type.Axioms Z 0 Z.add Z.add_assoc Z.add_0_l Z.add_0_r.

@@

Definition Z_Ring_axioms : Ring_of_Monoid.axioms Z _ :=                        #\label{demo:theory:z:ring:axioms}#
  Ring_of_Monoid.Axioms Z 1 Z.opp Z.mul
    Z.add_opp_diag_l Z.add_opp_diag_r Z.mul_assoc Z.mul_1_l Z.mul_1_r
    Z.mul_add_distr_r Z.mul_add_distr_l.

@@

We use the \coq{Monoid_of_Type.Axioms} \emph{\phantterm{}}
(line~\ref{demo:theory:z:monoid:axioms})
in order to build an instance of the \coq{Monoid}
structure for binary integers \coq{Z}.
We then register that monoid instance as the canonical one on \coq{Z}
(line~\ref{demo:theory:z:monoid:canonical}) via the command
\coq{hb.canonical}.
We can similarly declare that \coq{Z} forms a ring by using
the \coq{Ring_of_Monoid.Axioms} \phantterm{}
(lines~\ref{demo:theory:z:ring:axioms} and~\ref{demo:theory:z:ring:canonical}).
Note that the \coq{Ring_of_Monoid.Axioms} \phantterm{} is not
a plain record constructor for \coq{Ring_of_Monoid.axioms}, since that
would require more arguments, namely the monoid ones (see the \coq{_}
at line~\ref{demo:theory:z:ring:axioms}). The
\phantterm{} synthesized by \HB{} infers them automatically
(as in~\cite[Section 7]{DBLP:conf/itp/MahboubiT13}) thanks to the \coq{hb.canonical}
declaration given just above.

@@

\begin{coqcode}
#\hbmixin{}# Record Monoid_of_Type A := { ... (* unchanged *) ... }.
#\hbstructure{}# Definition Monoid := { A & Monoid_of_Type.axioms A }.

#\hbmixin{}# Record AbelianGroup_of_Monoid A of Monoid.axioms A := {
  opp : A -> A;
  addrC : commutative (add : A -> A -> A);
  addNr : left_inverse zero opp add;
}.
#\hbstructure{}# Definition AbelianGroup :=
  { A of Monoid.axioms A & AbelianGroup_of_Monoid.axioms A }.

#\hbmixin{}# Record Ring_of_AbelianGroup A of AbelianGroup.axioms A := {
  one : A;
  mul : A -> A -> A;
  mulrA : associative mul;
  mul1r : left_id one mul;              mulr1 : right_id one mul;
  mulrDl : left_distributive mul add;   mulrDr : right_distributive mul add;
}.
#\hbstructure{}# Definition Ring :=
  { A of AbelianGroup.axioms A & Ring_of_AbelianGroup.axioms A }.

@@

With this new version of the hierarchy, that we name V2, code written
for version V1 breaks. For example the declaration of the canonical ring over
the integers fails, if only
because we do not have a \coq{Ring_of_Monoid.Axioms} \phantterm{} anymore.

@@

\begin{coqcode}
#\hbfactory{}# Record Ring_of_Monoid A of Monoid.axioms A := {
  ... (* unchanged, see page 2 line 13 *) ...
}.
#\hbbuilders{}# Context A (f : Ring_of_Monoid.axioms A).                          #\label{demo3:variable:f}#

@@

  Definition to_AbelianGroup_of_Monoid :=
    AbelianGroup_of_Monoid.Axioms A (opp f) addrC (addNr f). (* addrN unused *)
  #\hbinstance{}# A to_AbelianGroup_of_Monoid.

  Definition to_Ring_of_AbelianGroup :=
    Ring_of_AbelianGroup.Axioms A (one f) (mul f)
      (mulrA f) (mul1r f) (mulr1 f) (mulrDl f) (mulrDr f).
  #\hbinstance{}# A to_Ring_of_AbelianGroup.

@@

The record \coq{Ring_of_Monoid.axioms} is the same we declared as a \mixin{}
in version V1. In order to make a \factory{} out of it we equip it with
two definitions that embody the \emph{\builder{}s}.
The first is \coq{to_AbelianGroup_of_Monoid} and
explains how to build an \coq{AbelianGroup} structure out of the \factory{}
axioms (named \coq{f}, line~\ref{demo3:variable:f}).
This construction is also registered as canonical for \coq{A},
so that the next construction \coq{to_Ring_of_AbelianGroup} can call
the \coq{Ring_of_AbelianGroup.Axioms} \phantterm{} that requires \coq{A} to be
an \coq{AbelianGroup}.
It is worth pointing out that the proof of \coq{addrC} we had in V1 is now
required in order to write the \builder{} for Abelian groups, while
the \coq{addrN} field is not used (the same statement is already part of
the theory of Abelian groups, see line~\ref{demo2:proof:addrN} of the previous
code snippet).

Thanks to this \factory{} we can now declare \coq{Z} to be an instance
of a ring using the \coq{Ring_of_Monoid.Axioms} \phantterm{}.
The associated \builder{}s generate, behind the scenes, instances of the
\coq{Ring_of_AbelianGroup.axioms} and \coq{AbelianGroup_of_Monoid.axioms} \mixins{}
that in turn are used to build instances of the \coq{AbelianGroup} and \coq{Ring}
structures. Indeed, when used in the context of the hierarchy version V3,
the command \hbinstance{} \coq{Z Z_Ring_axioms}
makes \coq{Z} an instance of \emph{both} structures, and not just the \coq{Ring}
one as in version V1.
Thanks to that the proof of \coq{example} can use the theory of
both structures, for example \coq{addrC} holds on Abelian groups,
\coq{addrA} holds on monoids, while \coq{addr1} holds on rings.
As a result the very same proof works on both
version V1 and V3.

@@

\begin{coqcode}
#\hbstructure{}# Definition Ring :=
  { A of Monoid.axioms A & Ring_of_Monoid.axioms A }.
#\hbstructure{}# Definition Ring :=
  { A of AbelianGroup.axioms A & Ring_of_AbelianGroup.axioms A }.
\end{coqcode}

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M.axioms}, which depends on the \mixins{}
  \(\requires{}(\coq{M.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\), and registers this
  new record both as a \mixin{} and a \factory{}. It also creates a
  \phantterm{} \coq{M.Axioms.}
\end{command}

@@

\begin{command} to declare a new \factory{} and generate new \mixinbuilders:
\begin{coqcode}
#\hbfactory{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
#\hbbuilders{}# Context T (a : M.axioms A).

  Definition #$b_{n+1}$# : #$f_{n+1}$# T .. := ...
  #\hbinstance{}# T #$b_{n+1}$#.
  ..
  Definition #$b_{n+k}$# : #$f_{n+k}$# T .. := ...
  #\hbinstance{}# T #$b_{n+k}$#.
#\hbend{}#.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M.axioms}, which depends on the mixins
  \(\requires{}(\coq{M.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\) and registers this
  new record as a factory. We then use the \factoryinstances{}
  \(b_{n+1}, \ldots, b_{n+k}\) provided by the user and derive
  \mixinbuilders{} from them, so that
  \(\provides{}(\coq{M.axioms}) = \provides{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right).\)

@@

We describe mathematical structures with three kinds of dependent records: mixins, classes, and structures.
As shown in section \ref{sec:example}, a \mixin{} gathers operators and axioms newly introduced by a structure.
As in \cite[section 2.4]{DBLP:conf/tphol/GarillotGMR09}\cite[section 2]{KSdraft}, a class record is parametrized by the carrier type \coq{(T : Type)} and gathers all the operators and axioms of a structure by assembling mixins, and a \coq{Structure type} (a record) bundles a carrier and its class instance, as follows.
\begin{coqcode}
Module Monoid.
Record axioms (T : Type) : Type :=
  Class { Monoid_of_Type_mixin : Monoid_of_Type.axioms T; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Monoid.
\end{coqcode}
The \coq{Monoid} module plays the role of a name space and forces us to write
qualified names such as \coq{Monoid.type}; as a consequence we can reuse the
same unqualified names for other structures, i.e., class and structure record
can always be named as \coq{axioms} and \coq{type} respectively.

@@

Next we define Abelian groups.
Since the monoid structure is the bottom of this hierarchy its class record
\coq{Monoid.axioms} consists just one \mixin{}. In contrast the class record
of Abelian groups consists of two \mixins{} where the second one depends
 on the former (since Abelian groups inherit from monoids).
\begin{coqcode}
Module AbelianGroup.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type.axioms T;
  AbelianGroup_of_Monoid_mixin : AbelianGroup_of_Monoid.axioms T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort }.
End AbelianGroup.
\end{coqcode}
As in the monoid structure, we declare \coq{AbelianGroup.sort} as an implicit
coercion and lift additive inverse \coq{opp} and Abelian group axioms.
Since Abelian groups inherit from monoids, we also declare an implicit coercion
from Abelian groups to monoids. A coercion between structures can be defined
in two steps: first a coercion between the class record of the
superclass to the class record of the subclass (line~\ref{demo4:coe:ag:monoid:class});
and a coercion between
structure records (line~\ref{demo4:coe:ag:monoid:type}) relying on the first one.
\begin{coqcode}
Coercion AbelianGroup.sort : AbelianGroup.type >-> Sortclass.
Coercion AbelianGroup_class_to_Monoid_class (T : Type) (c : AbelianGroup.axioms T) : #\label{demo4:coe:ag:monoid:class}#
  Monoid.axioms T := Monoid.Class T (AbelianGroup.Monoid_of_Type_mixin T c).
Coercion AbelianGroup_to_Monoid (T : AbelianGroup.type) : Monoid.type := #\label{demo4:coe:ag:monoid:type}#
  Monoid.Pack (AbelianGroup.sort T) (AbelianGroup.class T).

@@

\begin{wrapfigure}[3]{r}{.4\textwidth}
 \includegraphics[width=.4\textwidth]{v4.pdf}
 \caption{V4 introduces multiple inheritance. For brevity we omit the factories/builders for the upper arrows.}
 \label{fig:puzzle_v4}
\end{wrapfigure}
\
\begin{coqcode}
#\hbmixin{}# Record SemiRing_of_Monoid A 
    of Monoid.axioms A := {
  one : A;
  mul : A -> A -> A;
  (* 7 axioms are omitted. *)
}.

#\hbfactory{}# Record Ring_of_AbelianGroup A
    of AbelianGroup.axioms A := {
  (* 2 operators and 5 axioms are omitted. *)
}.
#\hbbuilders{}# Context A (a : Ring_of_AbelianGroup A).
..
#\hbend{}#.
\end{coqcode}

Since semirings and Abelian groups do not inherit from each other,
the definition of semirings and Abelian groups are quite similar:
\begin{coqcode}
Module SemiRing.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type.axioms T;
  SemiRing_of_Monoid_mixin : SemiRing_of_Monoid.axioms T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End SemiRing.
\end{coqcode}
We define implicit coercions from the semiring structure to the carrier
and the monoid structure, and we lift semiring operators and axioms as follows:
\begin{coqcode}
Coercion SemiRing.sort : SemiRing.type >-> Sortclass.
Coercion SemiRing_to_Monoid : SemiRing.type >-> Monoid.type.

@@

The class record is defined by gathering the monoid, Abelian group, and
semiring \mixins{}. Since the rings inherit from monoids, semirings, and
Abelian groups, we define implicit coercions from the ring structure to those
three structures.
\begin{coqcode}
Module Ring.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type.axioms T;
  SemiRing_of_Monoid_mixin : SemiRing_of_Monoid.axioms T Monoid_of_Type_mixin;
  AbelianGroup_of_Monoid_mixin : AbelianGroup_of_Monoid.axioms T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Ring.

>>>>

The first version of our hierarchy (that we name V1) features only two
structures: \coq{Monoid} and \coq{Ring}.
%\marginpar{remove hb.end for \mixins{}, use next release of coq elpi}
\begin{coqcode}
#\hbmixin{}# Record Monoid_of_Type A := {                       #\label{demo:mixin:mot}#
  zero : A;
  add : A -> A -> A;
  addrA : associative add;             (* `add` is associative.                   *)
  add0r : left_id zero add;            (* `zero` is the left and right neutral    *)
  addr0 : right_id zero add;           (*   element with respect to `add`.        *)
}.                                                             #\label{demo:mixin:mot:end}#
#\hbstructure{}# Definition Monoid := { A of Monoid_of_Type A }.        #\label{demo:structure:monoid}#

#\hbmixin{}# Record Ring_of_Monoid A of Monoid A := {       #\label{demo:mixin:rom}#
  one : A;
  opp : A -> A;
  mul : A -> A -> A;
  addNr : left_inverse zero opp add;   (* `opp x` is the left and right additive  *)
  addrN : right_inverse zero opp add;  (*   inverse of `x`.                       *)
  mulrA : associative mul;             (* `mul` is associative.                   *)
  mul1r : left_id one mul;             (* `one` is the left and right neutral     *)
  mulr1 : right_id one mul;            (*   element with respect to `mul`.        *)
  mulrDl : left_distributive mul add;  (* `mul` is left and right distributive    *)
  mulrDr : right_distributive mul add; (*   over `add`.                           *)
}.
#\hbstructure{}# Definition Ring := { A of Monoid A & Ring_of_Monoid A }. #\label{demo:structure:ring}#

@@

Line~\ref{demo:mixin:rom} declares a second \mixin{} collecting the operations
and properties that are needed in order to enrich a monoid to a ring, hence
the name \coq{Ring_of_Monoid}. Indeed this time the type variable \coq{A}
is followed by \coq{Monoid} that enriches
\coq{A} with the operations and properties of monoids. As a consequence
\coq{add} and \coq{zero} can be used to express the new properties.

@@

Definition Z_Monoid_axioms : Monoid_of_Type Z :=                         #\label{demo:theory:z:monoid:axioms}#
  Monoid_of_Type.Build Z 0 Z.add Z.add_assoc Z.add_0_l Z.add_0_r.

@@

Definition Z_Ring_axioms : Ring_of_Monoid Z _ :=                        #\label{demo:theory:z:ring:axioms}#
  Ring_of_Monoid.Build Z 1 Z.opp Z.mul
    Z.add_opp_diag_l Z.add_opp_diag_r Z.mul_assoc Z.mul_1_l Z.mul_1_r
    Z.mul_add_distr_r Z.mul_add_distr_l.

@@

We use the \coq{Monoid_of_Type.Build} \emph{\phantterm{}}
(line~\ref{demo:theory:z:monoid:axioms})
in order to build an instance of the \coq{Monoid}
structure for binary integers \coq{Z}.
We then register that monoid instance as the canonical one on \coq{Z}
(line~\ref{demo:theory:z:monoid:canonical}) via the command
\coq{hb.canonical}.
We can similarly declare that \coq{Z} forms a ring by using
the \coq{Ring_of_Monoid.Build} \phantterm{}
(lines~\ref{demo:theory:z:ring:axioms} and~\ref{demo:theory:z:ring:canonical}).
Note that the \coq{Ring_of_Monoid.Build} \phantterm{} is not
a plain record constructor for \coq{Ring_of_Monoid}, since that
would require more arguments, namely the monoid ones (see the \coq{_}
at line~\ref{demo:theory:z:ring:axioms}). The
\phantterm{} synthesized by \HB{} infers them automatically
(as in~\cite[Section 7]{DBLP:conf/itp/MahboubiT13}) thanks to the \coq{hb.canonical}
declaration given just above.

@@

\begin{coqcode}
#\hbmixin{}# Record Monoid_of_Type A := { ... (* unchanged *) ... }.
#\hbstructure{}# Definition Monoid := { A of Monoid_of_Type A }.

#\hbmixin{}# Record AbelianGroup_of_Monoid A of Monoid A := {
  opp : A -> A;
  addrC : commutative (add : A -> A -> A);
  addNr : left_inverse zero opp add;
}.
#\hbstructure{}# Definition AbelianGroup := { A of Monoid A & AbelianGroup_of_Monoid A }.

#\hbmixin{}# Record Ring_of_AbelianGroup A of AbelianGroup A := {
  one : A;
  mul : A -> A -> A;
  mulrA : associative mul;
  mul1r : left_id one mul;              mulr1 : right_id one mul;
  mulrDl : left_distributive mul add;   mulrDr : right_distributive mul add;
}.
#\hbstructure{}# Definition Ring := { A of AbelianGroup A & Ring_of_AbelianGroup A }.

@@

With this new version of the hierarchy, that we name V2, code written
for version V1 breaks. For example the declaration of the canonical ring over
the integers fails, if only
because we do not have a \coq{Ring_of_Monoid.Build} \phantterm{} anymore.

@@

\begin{coqcode}
#\hbfactory{}# Record Ring_of_Monoid A of Monoid A := {
  ... (* unchanged, see page 2 line 13 *) ...
}.
#\hbbuilders{}# Context A (f : Ring_of_Monoid A).                          #\label{demo3:variable:f}#

@@

  Definition to_AbelianGroup_of_Monoid :=
    AbelianGroup_of_Monoid.Build A (opp f) addrC (addNr f). (* addrN unused *)
  #\hbinstance{}# A to_AbelianGroup_of_Monoid.

  Definition to_Ring_of_AbelianGroup :=
    Ring_of_AbelianGroup.Build A (one f) (mul f)
      (mulrA f) (mul1r f) (mulr1 f) (mulrDl f) (mulrDr f).
  #\hbinstance{}# A to_Ring_of_AbelianGroup.

@@

The record \coq{Ring_of_Monoid} is the same we declared as a \mixin{}
in version V1. In order to make a \factory{} out of it we equip it with
two definitions that embody the \emph{\builder{}s}.
The first is \coq{to_AbelianGroup_of_Monoid} and
explains how to build an \coq{AbelianGroup} structure out of the \factory{}
axioms (named \coq{f}, line~\ref{demo3:variable:f}).
This construction is also registered as canonical for \coq{A},
so that the next construction \coq{to_Ring_of_AbelianGroup} can call
the \coq{Ring_of_AbelianGroup.Build} \phantterm{} that requires \coq{A} to be
an \coq{AbelianGroup}.
It is worth pointing out that the proof of \coq{addrC} we had in V1 is now
required in order to write the \builder{} for Abelian groups, while
the \coq{addrN} field is not used (the same statement is already part of
the theory of Abelian groups, see line~\ref{demo2:proof:addrN} of the previous
code snippet).

Thanks to this \factory{} we can now declare \coq{Z} to be an instance
of a ring using the \coq{Ring_of_Monoid.Build} \phantterm{}.
The associated \builder{}s generate, behind the scenes, instances of the
\coq{Ring_of_AbelianGroup} and \coq{AbelianGroup_of_Monoid} \mixins{}
that in turn are used to build instances of the \coq{AbelianGroup} and \coq{Ring}
structures. Indeed, when used in the context of the hierarchy version V3,
the command \hbinstance{} \coq{Z Z_Ring_axioms}
makes \coq{Z} an instance of \emph{both} structures, and not just the \coq{Ring}
one as in version V1.
Thanks to that the proof of \coq{example} can use the theory of
both structures, for example \coq{addrC} holds on Abelian groups,
\coq{addrA} holds on monoids, while \coq{addr1} holds on rings.
As a result the very same proof works on both
version V1 and V3.

@@

\begin{coqcode}
#\hbstructure{}# Definition Ring := { A of Monoid A & Ring_of_Monoid A }.
#\hbstructure{}# Definition Ring := { A of AbelianGroup A & Ring_of_AbelianGroup A }.
\end{coqcode}

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M}, which depends on the \mixins{}
  \(\requires{}(\coq{M}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\), and registers this
  new record both as a \mixin{} and a \factory{}. It also creates a
  \phantterm{} \coq{M.Build.}
\end{command}

@@

\begin{command} to declare a new \factory{} and generate new \mixinbuilders:
\begin{coqcode}
#\hbfactory{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
#\hbbuilders{}# Context T (a : M A).

  Definition #$b_{n+1}$# : #$f_{n+1}$# T .. := ...
  #\hbinstance{}# T #$b_{n+1}$#.
  ..
  Definition #$b_{n+k}$# : #$f_{n+k}$# T .. := ...
  #\hbinstance{}# T #$b_{n+k}$#.
#\hbend{}#.
\end{coqcode}
  Creates a module \coq{M} with a record
  \coq{M}, which depends on the mixins
  \(\requires{}(\coq{M}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\) and registers this
  new record as a factory. We then use the \factoryinstances{}
  \(b_{n+1}, \ldots, b_{n+k}\) provided by the user and derive
  \mixinbuilders{} from them, so that
  \(\provides{}(\coq{M}) = \provides{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right).\)

@@

We describe mathematical structures with three kinds of dependent records: mixins, classes, and structures.
As shown in section \ref{sec:example}, a \mixin{} gathers operators and axioms newly introduced by a structure.
As in \cite[section 2.4]{DBLP:conf/tphol/GarillotGMR09}\cite[section 2]{KSdraft}, a class record is parametrized by the carrier type \coq{(T : Type)} and gathers all the operators and axioms of a structure by assembling mixins, and a \coq{Structure type} (a record) bundles a carrier and its class instance, as follows.
\begin{coqcode}
Module Monoid.
Record axioms (T : Type) : Type :=
  Class { Monoid_of_Type_mixin : Monoid_of_Type T; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Monoid.
\end{coqcode}
The \coq{Monoid} module plays the role of a name space and forces us to write
qualified names such as \coq{Monoid.type}; as a consequence we can reuse the
same unqualified names for other structures, i.e., class and structure record
can always be named as \coq{axioms} and \coq{type} respectively.

@@

Next we define Abelian groups.
Since the monoid structure is the bottom of this hierarchy its class record
\coq{Monoid} consists just one \mixin{}. In contrast the class record
of Abelian groups consists of two \mixins{} where the second one depends
 on the former (since Abelian groups inherit from monoids).
\begin{coqcode}
Module AbelianGroup.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type T;
  AbelianGroup_of_Monoid_mixin : AbelianGroup_of_Monoid T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort }.
End AbelianGroup.
\end{coqcode}
As in the monoid structure, we declare \coq{AbelianGroup.sort} as an implicit
coercion and lift additive inverse \coq{opp} and Abelian group axioms.
Since Abelian groups inherit from monoids, we also declare an implicit coercion
from Abelian groups to monoids. A coercion between structures can be defined
in two steps: first a coercion between the class record of the
superclass to the class record of the subclass (line~\ref{demo4:coe:ag:monoid:class});
and a coercion between
structure records (line~\ref{demo4:coe:ag:monoid:type}) relying on the first one.
\begin{coqcode}
Coercion AbelianGroup.sort : AbelianGroup.type >-> Sortclass.
Coercion AbelianGroup_class_to_Monoid_class (T : Type) (c : AbelianGroup T) : #\label{demo4:coe:ag:monoid:class}#
  Monoid T := Monoid.Class T (AbelianGroup.Monoid_of_Type_mixin T c).
Coercion AbelianGroup_to_Monoid (T : AbelianGroup.type) : Monoid.type := #\label{demo4:coe:ag:monoid:type}#
  Monoid.Pack (AbelianGroup.sort T) (AbelianGroup.class T).

@@

\begin{wrapfigure}[3]{r}{.4\textwidth}
 \includegraphics[width=.4\textwidth]{v4.pdf}
 \caption{V4 introduces multiple inheritance. For brevity we omit the factories/builders for the upper arrows.}
 \label{fig:puzzle_v4}
\end{wrapfigure}
\
\begin{coqcode}
#\hbmixin{}# Record SemiRing_of_Monoid A 
    of Monoid A := {
  one : A;
  mul : A -> A -> A;
  (* 7 axioms are omitted. *)
}.

#\hbfactory{}# Record Ring_of_AbelianGroup A
    of AbelianGroup A := {
  (* 2 operators and 5 axioms are omitted. *)
}.
#\hbbuilders{}# Context A (a : Ring_of_AbelianGroup A).
..
#\hbend{}#.
\end{coqcode}

Since semirings and Abelian groups do not inherit from each other,
the definition of semirings and Abelian groups are quite similar:
\begin{coqcode}
Module SemiRing.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type T;
  SemiRing_of_Monoid_mixin : SemiRing_of_Monoid T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End SemiRing.
\end{coqcode}
We define implicit coercions from the semiring structure to the carrier
and the monoid structure, and we lift semiring operators and axioms as follows:
\begin{coqcode}
Coercion SemiRing.sort : SemiRing.type >-> Sortclass.
Coercion SemiRing_to_Monoid : SemiRing.type >-> Monoid.type.

@@

The class record is defined by gathering the monoid, Abelian group, and
semiring \mixins{}. Since the rings inherit from monoids, semirings, and
Abelian groups, we define implicit coercions from the ring structure to those
three structures.
\begin{coqcode}
Module Ring.
Record axioms (T : Type) : Type := Class {
  Monoid_of_Type_mixin : Monoid_of_Type T;
  SemiRing_of_Monoid_mixin : SemiRing_of_Monoid T Monoid_of_Type_mixin;
  AbelianGroup_of_Monoid_mixin : AbelianGroup_of_Monoid T Monoid_of_Type_mixin; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Ring.
